---
title: "E2_Presentation"
author: "Erin and Elizabeth"
date: "7/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```
```{r, include=FALSE}
setwd("/nfs/waterconflictafrica-data/Institute2019/Data/")
ACLED_Northern<-read.csv("ACLED9719_Northern_Africa.csv")
ACLED_Eastern<-read.csv("ACLED9719_Eastern_Africa.csv")
ACLED_Central<-read.csv("ACLED9719_Middle_Africa.csv")
ACLED_Western<-read.csv("ACLED9719_Western_Africa.csv")
ACLED_Southern<-read.csv("ACLED9719_Southern_Africa.csv")

conflict<-rbind(ACLED_Northern, ACLED_Eastern, ACLED_Central, ACLED_Western, ACLED_Southern)

```


## R Markdown

Pursuit: A socio-environmental synthesis of the linkages between water scarcity induced conflict and land use/land cover change in Africa to enhance multi-scalar decision making

Dataset: Armed Conflict Location & Event Data Project (ACLED)
Purpose: collection, analysis and mapping of political violence and protest
Geographies: 
-Africa
-South Asia
-South East Asia
-the Middle East
-Europe
-Latin America


```{r}
summary(conflict$event_type)
```

## Including Plots

You can also embed plots, for example:

```{r conflict, echo=FALSE}
ggplot(conflict, aes(x = year)) +
  geom_histogram(bins=19)

```

